---
output: html_document
runtime: shiny
---
<style TYPE="text/css">
code.has-jax {font: inherit; font-size: 2em; background: inherit; border: inherit;}
</style>
<script type="text/x-mathjax-config">
MathJax.Hub.Config({
    tex2jax: {
        inlineMath: [['$','$'], ['\\(','\\)']],
        skipTags: ['script', 'noscript', 'style', 'textarea', 'pre'] // removed 'code' entry
    }
});
MathJax.Hub.Queue(function() {
    var all = MathJax.Hub.getAllJax(), i;
    for(i = 0; i < all.length; i += 1) {
        all[i].SourceElement().parentNode.className += ' has-jax';
    }
});
</script>
<script type="text/javascript" src="http://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"></script>

## Application purpose 

The **SpNetPrep** package does not deal with statistics, but with the previous steps that can be required in order to perform a spatial statistical analysis of a point pattern that lies on a linear network representing a road structure. In this regard, the name chosen for the package summarizes its main goal of "Spatial Network Preprocessing" (**SpNetPrep**). The main feature provided by the **SpNetPrep** package is an interactive application that allows to carry out the complete preprocessing of a linear network that comes from a road structure. 

According to the technical difficulties that the development of a spatial analysis over a linear network implies, the **SpNetPrep** takes advantage of the R packages **leaflet** and **shiny** to provide an intuitive application that helps to reduce such difficulties.

Specifically, the **SpNetPrep** package focuses on the following parts of the preprocessing process that could be required prior to any spatial analysis over a linear network: **network creation and edition**, **network direction endowment** and **point pattern revision and modification**.

## Get the application

__Install the SpNetPrep package in R__

```{r, eval=T}
install.packages("SpNetPrep")
```

__Load the application__

```{r, eval=T}
library(SpNetPrep)
runAppSpNetPrep()
```

## Basic actions

The application included in **SpNetPrep** is divided into three sections: "Network Edition", "Network Direction" and "Point Pattern Revision". Now, it is briefly described how to use the options contained in each of these sections.

__NETWORK EDITION__

**Join vertex**: Click *vertex 1* and *vertex 2* of the linear network to make them connected by an edge

**Remove edge**: Click on the *edge* to be removed (anywhere along its length)

**Add point (+edge)**: *First* click on a *point of the map* (where there is no vertex nor edge) and *second click* on a *vertex already existing in the network* to make both points connected by an edge

**Add two points (+edge)**: Click on *two points of the map* (where there is no vertex nor edge) consecutively and the two points will be created and connected by an edge

The execution of these steps is marked in the map (green for additions, red for removals). Pressing the button "Rebuild linear network" makes these modifications of the linear network effective.

__NETWORK DIRECTION__

**Add flow**: Click *vertex 1* and *vertex 2* of the linear network *being connected by an edge*, and a flow *from* vertex 1 *to* vertex 2 will be defined

**Add long flow**: Click *vertex 1* and *vertex 2* of the linear network *not being connected by an edge*, and a flow *from* vertex 1 *to* vertex 2 will be defined taking the shortest path of the network (assuming all paths can be taken) that connects them

**Remove flow**: Click *vertex 1* and *vertex 2* of the linear network *being connected by an edge*, and the flow *from* vertex 1 *to* vertex 2 will be removed

**Remove long flow**: Click *vertex 1* and *vertex 2* of the linear network *not being connected by an edge*, and the flow *from* vertex 1 *to* vertex 2 that takes the shortest path of the network (assuming all paths can be taken) that connects them will be removed


__POINT PATTERN REVISION__

**Explore pattern**: Keep this option to explore the pattern and click the events located along the road network to see its marks attached (if the point pattern is marked)

**Remove point**: Click an *event* on the linear network to be moved an then on the point of the network (on an edge of the network) where it should be 

The execution of **Remove point** is not made effective until the user clicks the "Rebuild point pattern" button.





## Contact details

*&Aacute;lvaro Briz Red&oacute;n*

*Statistics and Operations Research, University of Val&egrave;ncia, Spain*

*alvaro.briz&#64;uv.es*
